Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
Correction for Radiation losses #6
change workflow images update CI/CD and workflow images #2

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}

@@

%% By default, llncs tocdepth value is 0, so only chapters and parts are shown in the ToC, but no sections and deeper levels of structure.
%% If \setcounter{tocdepth}{1} is used, the sections show up in the ToC.
%% I suggest to use \usepackage{tocbibind} in order to add the LoF and LoT in the ToC as well, if the ToC should not be listed itself, use \usepackage[nottoc]{tocbibind} instead.
%% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{1}
\usepackage[section,notlof,notlot,nottoc,]{tocbibind}

@@

%\tableofcontents
%\listoffigures
%\listoftables

@@

Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.

Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.

Implementing the proposed KUB workflow will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions. The project also focuses on enhancing the interactions between different environmental models to provide a holistic view of urban ecosystems.

This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

The workflow begins with collecting and preparing GIS and weather data and transforming them into a usable format for simulations. The transformed data are then partitioned for scalable processing and converted into Modelica and Feel++~\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the \textit{UBEM Generator}.

This processed data is employed to simulate energy consumption and indoor environmental quality using the \textit{Urban Building Energy Model (UBEM)}. The simulation focuses on a \textit{radiative heat transfer model}, enabling enhancement of the accuracy of the energy models. It also computes \textit{view factors} and \textit{shading masks}, assessing how buildings affect each other's exposure to natural light and heat and overall building energy needs, and the outdoor environment by influencing the urban heat island effect.

The building simulation outputs are then optionally fed into the \textit{Urban Air Pollution (UAP) simulator} to evaluate the impact of building emissions on urban air quality. A feedback loop refines the building simulation scenarios based on intermediate outputs from the \textit{UAP simulator}, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.

@@

The final step involves the \textit{UBEM Simulator}, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale. This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.

The described streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.

@@

This section provides an overview of the geometrical and physical modeling and simulation components of our urban building application.

@@

The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements. This section outlines the methodologies employed and the various Levels of Detail (LOD) used in the different models of kUB workflow.

@@

\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
\begin{itemize}
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{itemize}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

%\begin{wrapfigure}{R}{0.6\textwidth}
\begin{figure}[ht]
\centering
\subfloat[Representation of Strasbourg center with LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[Representation of Strasbourg center with LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[Representation of Grenoble LOD-1 terrain elevation\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.48\textwidth]{img-compressed-city-grenoble-terrain.png}
}

\caption{Various representations of cities and terrains}
\label{fig:city-strasbourg}
\vspace{-0.5cm}
\end{figure}
%\end{wrapfigure}

@@

Features using CGAL algorithms are not yet operational in our framework. We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world. The final mesh comprises all buildings in LOD-0 or LOD-1 and the terrain with elevation. The integration of all the urban components is currently being investigated. This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.

@@

\paragraph{Advancing Towards Full Parallelism}
The following steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI). The goal is to scale the process to handle entire cities or larger urban areas. This scale-up involves utilizing MPI to manage distributed computing resources effectively. To achieve the latter objective, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications. Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.

\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}

Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{itemize}
\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently. This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{itemize}

@@

We now turn to describing the physical modeling of city energy simulation.
To do this, we built on two main tools: Feel++ and Modelica. 
\subsubsection{Governing equation of the simulation}
The physical model of the city is based on a multizone model. One zone is allocated per building floor. The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
\begin{equation}
    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
\end{equation}
To give an overview of the equation's term we will give a brief summary.
\begin{itemize}
  \item $C\cdot \frac{dT}{dt}$ : thermal inertia of the construction. 
  \item $\phi_{HVAC}$ : energy output of the Heating Ventilation and Air Conditioning systems. 
  \item $\phi_{gain}$ : often reffered to as free energy gain, depends on solar gains, and building's occupation.
  \item $\phi_{losses}$ : energy losses throught wall/roof/slab, and air exchange.
\end{itemize}

\textbf{HVAC heatflow}

As for now we fixed the heating system as an ideal heat source.
Meaning the heatflow adapt to maintain a set temperature inside the building.

\textbf{Heat gain}

The heatflow gain is composed of solar gain and internal gain.

\textbf{Internal heat gain}

The internal heat gain are a function of human presence inside of a building :
\begin{equation}
  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
\end{equation}

\textbf{Solar heat gain}

The solar heat gain can be written as a sum of the different solar fluxes : direct, diffuse and reflected.
\begin{equation}
  \phi_{swl}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot 
\end{equation}

The direct solar radiation is written as such :
\begin{equation}
  E_{dir}=F_{dir}\cdot cos(I)
\end{equation}

$F_{dir}$ is a function of the horizontal solar radiation measured by a weather station.
\begin{equation}
  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
\end{equation}
\begin{equation}
  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
\end{equation}

The diffuse solar radiation is written as such :
\begin{equation}
  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
\end{equation}

The reflected solar radiation is written as such :
\begin{equation}
  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
\end{equation}

\textbf{Conduction losses}

\underline {I need to dive in the modelica model to extract the equation for the convection losses}

In this scenario we do not compute the thermal brige for the models.
\begin{equation}
  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
\end{equation}

\textbf{Radiation losses}

\underline{I'm not sure the Radiation exchange within a zone are taken into account, i need to check but i saw somewhere that} 
\underline{for LOD0-1 only the big wave length heatflow with external wall surface->sky are taken into account}
\begin{equation}
  \phi_{net,i}=\sum_{j\not=i}\frac{J_i-J_j}{\frac{1}{S_i\cdot F_{ij}}}
\end{equation}
\begin{equation}
  \phi_{net,i}=S_i\cdot \frac{\epsilon_i}{1-\epsilon_i}\cdot (\sigma\cdot T_i^4-J_i)
\end{equation}

\textbf{Air change}
\begin{equation}
  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
\end{equation}

@@

\begin{figure}[ht]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\section{CI/CD Framework for the Urban Building Pilot}
\label{sec:cicd-framework}

The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment. %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}

@@

\textbf{Nomenclature}

$\alpha$ : Absorption of a material.

$\beta$ : Angle of inclination of the wall to the horizontal.

$\Delta T$ : Temperature difference. [K]

$\epsilon$ : Emissivity of the surface.

$\phi_{air}$ : Air heatflow. [W]

$\phi_{net}$ : radiative heatflow. [W]

$\phi_{swl}$ : Solar heatflow from short wave lenght. [W]

$\phi_{wall}$ : Heatflow through a wall. [W]

$albedo$ : Reflective properties of the material.

$A_z$ : Azimuth of the surface.

$A_{zs}$ : Azimuth of the sun.

$C$ : Heatcapacity of the zone. [W$\cdot K^{-1}$]

$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.

$E_{dir}$ : Direct solar heatflow. [W$\cdot m^{-2}$]

$E_{dif}$ : Diffuse solar heatflow. [W$\cdot m^{-2}$]

$E_{ref}$ : Reflected solar heatflow. [W$\cdot m^{-2}$]

$F_{dir}$ : Direct solar radiation. [W$\cdot m^{-2}$]

$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data. [W$\cdot m^{-2}$]

$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.

$H_s$ : Angular height of the sun.

$J$ : Radiosity of a surface. [$W\cdot m^{-2}$]

$Met$ : Metabolic rate [W]

$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity [$W\cdot K^{-1}$]

$S$ : Surface. [$m^2$]

$U_j$ : Conductance of a $wall_j$. [$W\cdot m^{-2}\cdot K^{-1}$]

>>>>

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}

@@

%% By default, llncs tocdepth value is 0, so only chapters and parts are shown in the ToC, but no sections and deeper levels of structure.
%% If \setcounter{tocdepth}{1} is used, the sections show up in the ToC.
%% I suggest to use \usepackage{tocbibind} in order to add the LoF and LoT in the ToC as well, if the ToC should not be listed itself, use \usepackage[nottoc]{tocbibind} instead.
%% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{1}
\usepackage[section,notlof,notlot,nottoc,]{tocbibind}

@@

\tableofcontents
\listoffigures
%\listoftables

@@

Building on the foundations of the Feel++ framework, our project introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying these simulations at scale. Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.

Thanks to synergies with another CoE HiDALGO2 pilot, the KUB project is set to integrate building simulations with urban air pollution (UAP) models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.

Implementing these objectives will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions. The project also focuses on enhancing the interaction between different environmental models to provide a holistic view of urban ecosystems.

The paper is organized as follows: Section 2 discusses KUB's current workflow, Section 3 provides an overview of some modeling and simulation components, and finally, Section 4 delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with urban air pollution (UAP) models.

@@

The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations. This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.

This processed data is employed to simulate energy consumption and indoor environmental quality using the Urban Building Energy Model (UBEM). The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models. It also computes view factors and shading masks, assessing how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and overall building energy needs.

The building simulation outputs are then optionally fed into the urban air pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality. A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.

@@

The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale. This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.

This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.

@@

We now provide an overview of the geometrical and physical modeling and simulation components of the Urban building application.

@@

The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements. This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.

@@

\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

@@

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{wrapfigure}
In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply the following procedure:
\begin{itemize}
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{itemize}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in this geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas has a significant impact.
We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes both components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain.
And \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-0.png}
}
\hfill % Ensures that the images are placed side by side
\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-1.png}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
  \includegraphics[width=0.4\textwidth]{img-compressed-city-grenoble-terrain.png}
}

\caption{Various representations of cities and terrain. Representation of Strasbourg center with LOD-0 in the top left panel and LOD-1 in the top right. LOD-1 city (Grenoble, France) representation with terrain elevation.}
\label{fig:city-strasbourg}
\end{wrapfigure}

@@

All the features described above are not yet operational in our framework. We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world. The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation. The integration of all the urban components is currently being investigated. This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.

@@

\paragraph{Advancing Towards Full Parallelism}
The following steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI). The goal is to scale the process to handle entire cities or larger urban areas. This scale-up involves utilizing MPI to manage distributed computing resources effectively. To achieve this, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications. Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.

\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{itemize}
\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently. This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{itemize}

@@

We now turn to describing the physical modeling of city energy simulation.
To do this, we built on two main tools: Feel++ and Modelica.

@@

\begin{figure}[htbp]
\centering
\subfloat[LOD-0\label{fig:sm-building-east}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-east-facing.png}
}
\hfill
\subfloat[LOD-1\label{fig:sm-whole-building}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-whole-building.png}
}\\
\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-strasbourg.png}
}
\hfill
\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
  \includegraphics[width=0.45\textwidth]{img-compressed-view-factors-benchmark.png}
}
\caption{Solar masks and view factors computations}
\label{fig:solar-masks-vf}
\end{figure}

@@

\section{CI/CD Framework for the Urban Building Pilot}
The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment. %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}
\label{sec:benchmarking}

@@
